---
title: "DCC Brand Guidelines for ggplot"
author: "Laurence Horton"
date: "2022/05/16"
output: 
  html_document:
    css: style.css
---

```{r setup, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(fig.fullwidth = TRUE, echo = TRUE)
```

Load package library
```{r library, message = FALSE}
library(tidyverse)
```

## Modify an existing ggplot theme.  
Create a new theme for ggplot building on an existing theme, in this case theme_classic.
```{r Create a new theme}
theme_DCC <- function (base_size = 12,
                       base_family = "") {
  theme_classic() %+replace%
    theme(
      plot.background = element_rect(colour = "#ffffff"),
      # White
      legend.position = "bottom",
      # Legend at bottom of visualisation
      panel.grid.major  = element_line(colour = "#ffffff"),
      # White
      panel.background = element_rect(fill = "#ffffff", colour = "#ffffff"),
      # White
      panel.border = element_rect(colour = "#ffffff", fill = NA),
      # White
      axis.line = element_line(colour = "#97999B"),
      #Cool Gray 7
      axis.ticks = element_line(colour = "#97999B"),
      # Cool Gray 7
      axis.text = element_text(colour = "#75787B"),
      # Cool Gray 9
      text = element_text(family = "Proxima Nova", colour = "#75787B") # Cool Gray 9
    )
}
```

Create a vector for discrete category DCC colours. There's only eight colours here, and three of them are grey, so you will have to add more if needed.
```{r DCC colours}
DCC_colours <-
  c(
    "#DC6B2F",
    # Gold Drop
    "#ED8B00",
    # Tangerine
    "#F4DA40",
    # Golden Dream
    "#00B2A9",
    # Persian Green
    "#8E3A80",
    # Dark Purple
    "#75787B",
    # Cool Grey 9
    "#97999B",
    # Cool Grey 7
    "#BBBCBC"
  ) # Cool Gray 4
```

Load example data set.
```{r example data set}
data(mtcars)
mtcars <-
  rownames_to_column(mtcars, "car") # Extract car names from row names and add as a column
mtcars <- mtcars[c(1:7), ] # Keep only the first seven rows
```

## Example visualisations with DCC theme

You can of course alter elements of the visualisation, like removing background or grid lines, in ggplot.  

### Column
```{r column}
ggplot(mtcars, aes(car, mpg, fill = car)) +
  geom_col() +
  geom_text(
    aes(label = paste0(mpg)),
    position = position_stack(vjust = .925),
    size = 3,
    colour = "#000000"
  ) +
  theme_DCC() +
  scale_fill_manual(values = c(DCC_colours)) +
  labs(
    x = "Model of car",
    y = "Miles per gallon",
    title = "Cars and MPG",
    subtitle = "Yes, counting cars MPG",
    caption = "Source: mtcars dataset",
  )
```

## Plot
```{r plot}
ggplot(mtcars, aes(mpg, wt)) +
  geom_point(colour = "#DC6B2F", size = 4) +
  theme_DCC() +
  theme(
    panel.background = element_rect(fill = "#BBBCBC"),
    panel.grid.major  = element_line(colour = "#97999B"),
  ) +
  scale_fill_manual(values = c(DCC_colours)) +
  labs(
    x = "Weight of car",
    y = "Miles per gallon",
    title = "MPG and CYL",
    subtitle = "It's cars weight by MPG",
    caption = "Source: mtcars dataset"
  )
```

## Bar
```{r bar}
ggplot(mtcars, aes(x = "", fill = factor(mpg))) +
  geom_bar(width = .5) +
  scale_fill_manual(values = c(DCC_colours)) +
  theme_DCC() +
  theme(
    legend.position = "right",
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_blank()
  ) +
  labs(
    fill = "MPG",
    title = "Bar chart of MPG and cars",
    subtitle = "I don't really have a subtitle for this one",
    caption = "Source: mtcars dataset",
    x = NULL,
    y = NULL,
  ) +
  coord_flip()
```